A Documentary History of \\ the Nock Combinator Calculus

### 2025-07-18 mss.tex
Post
Add Curtis byline.
Realign

\newcommand{\authorname}{N. E. Davis}
\newcommand{\authorpatp}{\patp{lagrev-nocfep}}
\newcommand{\affiliation}{Zorp Corp}

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
            %   Manuscript submitted for review.\\
              {\it Urbit Systems Technical Journal} II:1 (2025):  153–188. \\
              ~ \\
              Address author correspondence to \authorpatp.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{A History of Nock}
\fancyfoot[LE,RO]{\thepage}

%%MANUSCRIPT
\title{A Documentary History of \\ the Nock Combinator Calculus}
\author{\authorname~\authorpatp \\ \affiliation}
\date{}

@@

\sloppy
The earliest extant Nock is \texttt{U}, a proto-Nock posted to the \textit{Lambda the Ultimate} blog in 2006 (\citet{Yarvin2006a}; \citet{Yarvin2006}).\footnote{Curtis Yarvin was consulted for elements of this history.  Unfortunately many elements of the original prehistory of Nock appear to be lost to the sands of time on unrecoverable hard drives.}  The draft is versioned 0.15; subsequent evidence indicates that this is a downward-counting kelvin-versioned document already.  The full specification is reproduced in Listing~\ref{lst:u}.
%Yarvin2006a, http://lambda-the-ultimate.org/node/1269
%Yarvin2006, https://web.archive.org/web/20060701070718/http://urbit.sourceforge.net/u.txt

@@

Opcodes were reordered slightly.  Compound opcodes were introduced, such as a conditional branch and a static hint opcode.

>>>>

\newcommand{\authorname}{N. E. Davis~\patp{lagrev-nocfep},\\Curtis Yarvin~\patp{sorreg-namtyv}}
\newcommand{\affiliation}{Zorp Corp, Urbit Foundation}

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
            %   Manuscript submitted for review.\\
              {\it Urbit Systems Technical Journal} II:1 (2025):  153–188. \\
              ~ \\
              Address author correspondence to \patp{lagrev-nocfep}.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{A History of Nock}
\fancyfoot[LE,RO]{\thepage}

%%MANUSCRIPT
\title{A Documentary History of \\ the Nock Combinator Calculus}
\author{\authorname \\ \affiliation}
\date{}

@@

\sloppy
The earliest extant Nock is \texttt{U}, a proto-Nock posted to the \textit{Lambda the Ultimate} blog in 2006 (\citet{Yarvin2006a}; \citet{Yarvin2006}).\footnote{Unfortunately many elements of the original prehistory of Nock appear to be lost to the sands of time on unrecoverable hard drives.}  The draft is versioned 0.15; subsequent evidence indicates that this is a downward-counting kelvin-versioned document already.  The full specification is reproduced in Listing~\ref{lst:u}.
%Yarvin2006a, http://lambda-the-ultimate.org/node/1269
%Yarvin2006, https://web.archive.org/web/20060701070718/http://urbit.sourceforge.net/u.txt

@@

Opcodes were reordered slightly.  Compound opcodes were introduced, such as a conditional branch and a static hint opcode.  Autocons appeared explicitly.
